\section*{Conclusion}
\addcontentsline{toc}{section}{Conclusion}

This report has detailed the design, implementation, and verification of a
robust University Sports Complex Management System. Our solution effectively
bridges the gap between theoretical database principles and practical
application development.

\subsection*{Summary of Achievements}
\begin{itemize}
    \item \textbf{Data Integrity:} We established a solid foundation using
    Domain, Entity, and Referential integrity constraints. As demonstrated in
    Task 1, these constraints act as the non-negotiable guardians of data
    quality, preventing invalid states (e.g., negative inventory or conflicting
    timestamps) even if the application layer fails.
    \item \textbf{SQL Proficiency vs. ORM:} Task 2 demonstrated the comprehensive implementation of the schema and complex data retrieval needs. While Django handles standard CRUD operations, our raw SQL queries (including Joins, Aggregates, and Subqueries) proved essential for generating advanced analytical reports that go beyond basic object retrieval.
    \item \textbf{Business Logic Enforcement:} In Task 3, we utilized SQL
    triggers to implement complex rules such as dynamic booking limits (max 2
    pending bookings) and cross-table validation (equipment availability). This
    ensures that business rules are consistent regardless of the access method.
    \item \textbf{Secure Access Control:} Task 4 showcased a defense-in-depth
    security strategy. By combining Role-Based Access Control (RBAC) with
    Row-Level Security views, we ensured that users like Coaches and Members
    operate within strictly defined boundaries, protecting sensitive data while
    maintaining usability.
    \item \textbf{Application Integration:} The integration with Django
    demonstrates the synergy between a powerful backend DBMS and a modern web
    framework. While Django provides a user-friendly interface and preliminary
    validation (e.g., form checks), the MySQL database serves as the ultimate
    source of truth and enforcement.
\end{itemize}

In conclusion, the system meets all specified requirements for data integrity,
security, and functionality. The "Database First" design philosophy ensures that
the system is reliable, scalable, and maintainable, capable of supporting the
dynamic operations of a busy sports complex.
